---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# phecodemap

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


## Overview

The phecodemap package builds a shiny app to visualize the hierarchy of 
PheCode Mapping with ICD-9 and ICD-10-cm. The same PheCode hierarchy is 
displayed in two ways: as a sunburst plot and as a tree.

## Installation



Install development version from GitHub:

```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("celehs/phecodemap")
```


## Usage

This is a basic example which shows you how to run the `phecodemap` app. Remember you need to get access to the data and save it to your local computer. In order to guarantee some dependencies are loaded, you must use *library(phecodemap)* beforehand, instead of directly running phecodemap::run_app(data_path).


```{r eval=FALSE}
library(shinyBS)
library(phecodemap)
run_app(data_path = "the path to the app data (Rada format)")
```



## App instructions

See the [App instructions](https://celehs.github.io/phecodemap/articles/main.html) guide to learn how to use the app.


## Citations

- Wei WQ, Bastarache LA, Carroll RJ, Marlo JE, Osterman TJ, Gamazon ER, Cox NJ, Roden DM, Denny JC. Evaluating phecodes, clinical classification software, and ICD-9-CM codes for phenome-wide association studies in the electronic health record. PLoS One. 2017 Jul 7;12(7):e0175508. https://doi.org/10.1371/journal.pone.0175508

- Wu, P., Gifford, A., Meng, X., Li, X., Campbell, H., Varley, T., Zhao, J., Carroll, R., Bastarache, L., Denny, J. C., Theodoratou, E., & Wei, W. Q. (2019). Mapping ICD-10 and ICD-10-CM Codes to Phecodes: Workflow Development and Initial Evaluation. JMIR medical informatics, 7(4), e14325. https://doi.org/10.2196/14325

